---
title: "Zooplanckton graphic description"
categories: 
  - "Graph + description (SDD)"
description: |
  Zooplankton dataset analysis and graphic description
author:
  - name: Elise Poiret
    url: {}
date: 12-15-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
SciViews::R
```

# Dataset description

```{r import}
zooplankton <- read("zooplankton", package = "data.io")
```

The dataset "zooplankton" discribed various features measured on a samples of zooplankton originating from Madagascar with R and ZooImage. It comes from Grosjean, Ph and K. Denis who supervised classification of images.

# The size of the different classes.

```{r graph}
chart(zooplankton, size  ~ class %col=% class) + 
  geom_point(show.legend = TRUE)
```
 
 
 The cnidrians are the biggest. After the cnidarians it is the chaetognathes and the fish who are the biggest. The smallest are the protists. We see a greater diversity of size in chaetognaths and cnidarians. 

